Methods and Results

### 2022-05-02 ms.Rmd
Cleaning up and updating code. Could use orchaRd now for much of it and I may instead change.

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, MuMIn, equatiomatic, magrittr, data.table)
eval(metafor:::.MuMIn)

```
```{r loaddata, echo = FALSE, results = "hide"}
################
# Tree
################
      source("./R/func.R")  
      data <- read.csv("./data/meta_data.csv")
      data <- data %>% 
              mutate(species2 = species, 
                     zSSD = scale(SSD_lnRR),
                     sex_life = log(M_lifespan / F_lifespan))

@@

###################
# Multilevel Meta-analytic Models (intercept only), plus robust variace estimation test.
###################

@@

# Table 1: Effect, confidemce intervals, prediction intervals, heterogenity
   hetero_table <- metaAidR::I2(model1.1, v = data$v_SMDH, obs = "obs") # Same as orchaRd::i2_ml(model1.1)    
   hetero_table_phylo <- metaAidR::I2(model1.2, v = data$v_SMDH, phylo = "species2", obs = "obs") # Same as orchaRd::i2_ml(model1.1)    
         table1 <- make_table(robust, heteroTable = hetero_table)

@@

  model1.1_pub_full <- rma.mv(SMDH ~ sqrt(inv_n_eff) + SSD_lnRR + Harm_type, V = data$v_SMDH, 
                              random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)

@@

  # Use raw SSD for plotting, so we can ployt raw data, which is easier to interpret
  model1.3_nonZ <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, 
                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
  robust_model1.3_nonZ <- robust(model1.3_nonZ, cluster = data$study)

@@

  # Marginalised Harmtype        
  model1.4 <- rma.mv(SMDH ~ Harm_type, V = data$v_SMDH, 
                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
  robust(model1.4, cluster = data$study)

@@

  # Model that contains harm type and SSD. Harmtype appears to have different variances, so I'll check whether it is safe to assume homogeneity of variance across groups
  model1.5 <- rma.mv(SMDH ~  Harm_type + zSSD, V = data$v_SMDH, 
                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
                     method = "ML", data = data)

@@

Using our MLMA models we also calculated effect size heterogenity using $I^2$ [@HigginsThompson; @nakagawa2012methodological]. $I^2_{study}$ and $I^2_{species}$ are defined as the proportion of effect size variance over total variance as a result of between study and species effects, respectively.In contrast, $I^2_{total}$ was calculated as the proportion of total effect size variance after accounting for, or removing, total sampling variance.

We explored drivers of effect size heterogenity using multi-level meta-regression (MLMR) models. Our models included fixed effects (i.e., moderators) that we *a priori* predicted would impact female fitness. More specifically, we predicted that the intensity of sexual selection and sexual conflict would affect how much harm males did to females. To test these predictions, we included an index of sexual size dimorphism (SSD), which involved taking the log transfomed ratio between male body size to female body size for the species (i.e.,  $log \left( \frac{Male_{body size}}{Female_{bodysize}} \right)$, hereafter referred to as SSD). Positive SSD values indicate species with larger males compared to females, whereas negative SSD values indicate species where females are larger than males. While this does not directly measure the intensity of sexual selection, it is a proxy for it, and has been used in numerous meta-analyses in the past (CITE).

In addition to SSD, we also categorised effect sizes as having come from species with different types of male harm and sperm competition intensity (see moderators section). These included species with direct male harm (i.e., species with traumatic insemination) as well as species with indirect male harm (i.e., species that harm females through harrassment). There are also a number of species where it is clear both direct and indirect forms of male harm exist. We also fit seperate models to a two-level categorical moderator describing the sperm competition intensity of the species (i.e, "high" or "low"). In both these models, we controlled for SSD index, but included z-transformed SSD, such that meta-analytic means in each categorical moderator are for species of average SSD. We also accounted for the possibility that SSD might vary dependeing on the specific harm type and sperm competition intensity (i.e., interaction between SSD and Harm type and Sperm competition intensity). We evaluated support for interactions by comparing a model including the interaction to a model without it, comparing $AIC_{c}$ between the two models. We chose the model with the lowest $AIC_{c}$ if they differed by greater than 2, otherwise, we choose the most parsimonious model. All models comparing fixed effects were fit with maximum likelihood for model comparison of fixed effect structure, and then subsequently re-fit with restricted maximum likelihood when the fixed effect structure was identified.

@@

```{r funnel, fig.height=7.62500, fig.width=14.90278, fig.cap="A) Funnel plot of effect size as a function of precision (i.e., inverse of sampling standard error). B) orchaRd plot of the overall meta-analytic mean efect size, 95% confidnece intervals (thick black bars) and 95% prediction intervals (whiskers)"}
p1 <- ggplot(data, aes(x = SMDH, y = 1 / sqrt(v_SMDH), xmin = -6, xmax = 6)) +
geom_point(aes(colour = class)) +
labs(x = "SMDH", 
	 y = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$"),
	 colour = "Class") +
scale_color_grey() + 
#scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9")) + 
theme_bw()

p2 <- orchard_plot(model1.1, mod = "Int", xlab = "SMDH") + 
      scale_colour_manual(values = "grey") + 
      scale_fill_manual(values = "red") +
      labs(y = "Overall Meta-analytic Mean") +
      scale_y_discrete(labels = "")

p1 + p2 + plot_annotation(tag_levels = c('A', 'B'))

```{r pretty_table}

autonum <- officer::run_autonum(seq_id = "tab", pre_label = "Table 1", bkm_all = TRUE)
ft <- flextable::flextable(table1)
ft <- flextable::set_caption(ft,  caption = "Effect size", autonum = autonum)
ft %>%
  flextable::compose(part = "header", j = "n", value = as_paragraph("n", as_sub("effects"))) %>%
  flextable::compose(part = "header", j = "std", value = as_paragraph("n", as_sub("studies"))) %>%
  flextable::compose(part = "header", j = "spp", value = as_paragraph("n", as_sub("species"))) %>%
  flextable::compose(part = "header", j = "est", value = as_paragraph("Meta-analytic mean")) %>%
  flextable::compose(part = "header", j = "CI", value = as_paragraph("95% CI")) %>%
  flextable::compose(part = "header", j = "PI", value = as_paragraph("95% PI")) %>%
  flextable::compose(part = "header", j = "i2_stdy", value = as_paragraph("I", as_sup("2"), as_sub("study"))) %>%
  flextable::compose(part = "header", j = "i2_trait", value = as_paragraph("I", as_sup("2"), as_sub("trait"))) %>%
  flextable::compose(part = "header", j = "i2_species", value = as_paragraph("I", as_sup("2"), as_sub("species"))) %>%
  flextable::compose(part = "header", j = "i2_tot", value = as_paragraph("I", as_sup("2"), as_sub("total")))

>>>>

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, MuMIn, equatiomatic, magrittr, data.table)
eval(metafor:::.MuMIn)
```

```{r loaddata, echo = FALSE, results = "hide"}
################
# Tree
################
      source("./R/func.R")  
      data <- read.csv("./data/meta_data.csv")
      data <- data %>% 
              mutate(species2 = species, 
                     zSSD = scale(SSD_lnRR),
                     sex_life = log(M_lifespan / F_lifespan))

@@

###################
# Multilevel Meta-analytic Models (intercept only), plus robust variance estimation test.
###################

@@

# Table 1: Effect, confidence intervals, prediction intervals, heterogeneity
   hetero_table <- metaAidR::I2(model1.1, v = data$v_SMDH, obs = "obs") # Same as orchaRd::i2_ml(model1.1)    
   hetero_table_phylo <- metaAidR::I2(model1.2, v = data$v_SMDH, phylo = "species2", obs = "obs") # Same as orchaRd::i2_ml(model1.1)    
         table1 <- make_table(robust, heteroTable = hetero_table)

@@

  model1.1_pub_full <- rma.mv(SMDH ~ sqrt(inv_n_eff) + SSD_lnRR + Harm_type, V = data$v_SMDH, 
                              random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
   model1.1_pub_full_het <- rma.mv(SMDH ~ sqrt(inv_n_eff) + SSD_lnRR + Harm_type, V = data$v_SMDH, 
                              random = list(~1|study, ~1|variable, ~1|species, ~Harm_type|obs), rho = 0, 
                              str = "HCS", test = "t", data = data)
      AICc(model1.1_pub_full, model1.1_pub_full_het) # Basically the same results so simplify model.

@@

  # Use raw SSD for plotting, so we can plot raw data, which is easier to interpret
  model1.3_nonZ <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, 
                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
  robust_model1.3_nonZ <- robust(model1.3_nonZ, cluster = data$study)

@@

  # Marginalised Harm type        
  model1.4 <- rma.mv(SMDH ~ Harm_type, V = data$v_SMDH, 
                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
  robust(model1.4, cluster = data$study)

@@

  # Model that contains harm type and SSD. Harm type appears to have different variances, so I'll check whether it is safe to assume homogeneity of variance across groups
  model1.5 <- rma.mv(SMDH ~  Harm_type + zSSD, V = data$v_SMDH, 
                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
                     method = "ML", data = data)

@@

Using our MLMA models we also calculated effect size heterogeneity using $I^2$ [@HigginsThompson; @nakagawa2012methodological]. $I^2_{study}$ and $I^2_{species}$ are defined as the proportion of effect size variance over total variance as a result of between study and species effects, respectively.In contrast, $I^2_{total}$ was calculated as the proportion of total effect size variance after accounting for, or removing, total sampling variance.

We explored drivers of effect size heterogeneity using multi-level meta-regression (MLMR) models. Our models included fixed effects (i.e., moderators) that we *a priori* predicted would impact female fitness. More specifically, we predicted that the intensity of sexual selection and sexual conflict would affect how much harm males did to females. To test these predictions, we included an index of sexual size dimorphism (SSD), which involved taking the log transformed ratio between male body size to female body size for the species (i.e.,  $log \left( \frac{Male_{body size}}{Female_{bodysize}} \right)$, hereafter referred to as SSD). Positive SSD values indicate species with larger males compared to females, whereas negative SSD values indicate species where females are larger than males. While this does not directly measure the intensity of sexual selection, it is a proxy for it, and has been used in numerous meta-analyses in the past (CITE).

In addition to SSD, we also categorised effect sizes as having come from species with different types of male harm and sperm competition intensity (see moderators section). These included species with direct male harm (i.e., species with traumatic insemination) as well as species with indirect male harm (i.e., species that harm females through harassment). There are also a number of species where it is clear both direct and indirect forms of male harm exist. We also fit separate models to a two-level categorical moderator describing the sperm competition intensity of the species (i.e, "high" or "low"). In both these models, we controlled for SSD index, but included z-transformed SSD, such that meta-analytic means in each categorical moderator are for species of average SSD. We also accounted for the possibility that SSD might vary depending on the specific harm type and sperm competition intensity (i.e., interaction between SSD and Harm type and Sperm competition intensity). We evaluated support for interactions by comparing a model including the interaction to a model without it, comparing $AIC_{c}$ between the two models. We chose the model with the lowest $AIC_{c}$ if they differed by greater than 2, otherwise, we choose the most parsimonious model. All models comparing fixed effects were fit with maximum likelihood for model comparison of fixed effect structure, and then subsequently re-fit with restricted maximum likelihood when the fixed effect structure was identified.

@@

```{r funnel, fig.height=7.62500, fig.width=14.90278, fig.cap="A) Funnel plot of effect size as a function of precision (i.e., inverse of sampling standard error). B) orchaRd plot of the overall meta-analytic mean efect size, 95% confidnece intervals (thick black bars) and 95% prediction intervals (whiskers)"}
p1 <- ggplot(data, aes(x = SMDH, y = 1 / sqrt(v_SMDH), xmin = -6, xmax = 6)) +
geom_point(aes(colour = class), size = 3) +
labs(x = "SMDH", 
	 y = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$"),
	 colour = "Class") +
scale_color_grey() + 
#scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9")) + 
theme_bw()

p2 <- orchard_plot(model1.1, mod = "1", group = "species", data = data, xlab = "SMDH") + 
      scale_colour_manual(values = "grey") + 
      scale_fill_manual(values = "red") +
      scale_y_discrete(labels = "")

p3 <- p1 + p2 + plot_annotation(tag_levels = c('A', 'B'))
p3
ggsave(plot = p3, filename = "fig1.png", width = 12, height= 5, path = "./output/figs", units = "in", device="png", dpi = 600)
```

```{r pretty_table, tab.cap = "Number of effect sizes, studies and species along with overall meta-analytic mean (average SMDH) and 95% confidence (CI) and prediction intervals (PI). Heterogeneity estimates and 95% CI's are also provided for study, trait, species and total heterogeneity (excluding sampling variance)"}

autonum <- officer::run_autonum(seq_id = "tab", pre_label = "Table 1", bkm_all = TRUE)
ft <- flextable::flextable(table1)
ft %>%
  flextable::compose(part = "header", j = "n", value = as_paragraph("n", as_sub("effects"))) %>%
  flextable::compose(part = "header", j = "std", value = as_paragraph("n", as_sub("studies"))) %>%
  flextable::compose(part = "header", j = "spp", value = as_paragraph("n", as_sub("species"))) %>%
  flextable::compose(part = "header", j = "est", value = as_paragraph("Meta-analytic mean")) %>%
  flextable::compose(part = "header", j = "CI", value = as_paragraph("95% CI")) %>%
  flextable::compose(part = "header", j = "PI", value = as_paragraph("95% PI")) %>%
  flextable::compose(part = "header", j = "i2_stdy", value = as_paragraph("I", as_sup("2"), as_sub("study"))) %>%
  flextable::compose(part = "header", j = "i2_trait", value = as_paragraph("I", as_sup("2"), as_sub("trait"))) %>%
  flextable::compose(part = "header", j = "i2_species", value = as_paragraph("I", as_sup("2"), as_sub("species"))) %>%
  flextable::compose(part = "header", j = "i2_tot", value = as_paragraph("I", as_sup("2"), as_sub("total")))
